prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-10-12 inst/MyArticle/paper.Rmd
adding benchmark based on cptac dataset
update vignettes

```{r prepro,  echo = TRUE , fig.cap="(ref:scaling)", out.width = '90%', fig.width = 8, fig.height = 8}
## load peptide level data
d <- prolfqua::old2new(prolfqua::prolfqua_data('data_ionstar')$filtered())
d <- prolfqua::LFQData$new(d$data, d$config)
## create R6 obejct
lfqd <- prolfqua::LFQData$new(d$data, d$config)

@@

```{r benchmarkROC}
ttt <- sapply(allBenchmarks, function(x){x$complete(FALSE)})
res <- purrr::map_df(allBenchmarks, function(x){x$pAUC()})
res <- res |> dplyr::mutate(whatfix = dplyr::case_when(what == "scaled.beta.based.significance" ~ "scaled.p.value", TRUE ~ what))

@@

# column with protein abundances
atable$set_work_intensity("total.intensity")

>>>>

```{r prepro,  echo = TRUE , fig.cap="(ref:scaling)", out.width = '90%', fig.width = 8, fig.height = 8}
## load peptide level data
d <- prolfqua::prolfqua_data('data_ionstar')$filtered()
d <- prolfqua::LFQData$new(d$data, prolfqua::old2new(d$config))
## create R6 obejct
lfqd <- prolfqua::LFQData$new(d$data, d$config)

@@

```{r benchmarkROC}
ttt <- sapply(allBenchmarks, function(x){x$complete(FALSE)})
names(allBenchmarks)

for(i in seq_along(allBenchmarks)) {
  allBenchmarks[[i]]$pAUC()
}

res <- purrr::map_df(allBenchmarks, function(x){x$pAUC()})
res <- res |> dplyr::mutate(whatfix = dplyr::case_when(what == "scaled.beta.based.significance" ~ "scaled.p.value", TRUE ~ what))

@@

# column with protein abundances
atable$set_response("total.intensity")
